FEM Model Analysis

### 2021-01-11 FEM_R/model_analysis.Rmd
Copied work on the AgeUK validation from the barebones FEM version over to development.

>>>>

# AgeUK Almanac External Validation

'The Age UK almanac of disease profiles in later life', published in October 2015, contains information on the prevalence of major diseases, conditions, and syndromes affecting older people in England, broken down by age and sex.

```{r}
# Need a function here to handle the repetition
get_prevalence <- function(FEM) {

}

# Now read in male and female AgeUK data
male_ageUK <- read.csv('../../Validation/AgeUK-chronDisease-MALE.csv')
female_ageUK <- read.csv('../../Validation/AgeUK-chronDisease-FEMALE.csv')
# Rename columns
colnames(male_ageUK) <- c('Condition', 'Age 60-64', 'Age 65-69', 'Age 70-74', 'Age 75-79', 'Age 80-84', 'Age 85-89', 'Age 90-94', 'Age 95-99', 'Age 100+', 'Total Pop.')
colnames(female_ageUK) <- colnames(male_ageUK)

# Collect conditions into a list for extracting from FEM
# Will need to be written in FEM shorthand
keep_vars <- c('male', 'age', 'hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'cancre', 'demene')

# Now get FEM output for 2014
FEM_2014 <- read_dta('ELSA_Baseline/detailed_output/y2014_rep1.dta')
FEM_2014 <- FEM_2014[keep_vars]
# extract males and females
mFEM_2014 <- FEM_2014 %>% filter(male == 1)
fFEM_2014 <- FEM_2014 %>% filter(male == 0)

m6064 <- mFEM_2014 %>% filter(age %in% (60:64))
f6064 <- fFEM_2014 %>% filter(age %in% (60:64))

m6064_prev <- data.frame((colSums(m6064) / nrow(m6064)) * 100)
f6064_prev <- data.frame((colSums(f6064) / nrow(f6064)) * 100)
colnames(m6064_prev) <- 'FEM_male_6064'
colnames(f6064_prev) <- 'FEM_female_6064'

prev_df <- data.frame(m6064_prev, f6064_prev)

# correct colnames in ageUK stuff
male_ageUK <- male_ageUK %>% filter(conditions == c('Hypertension', 'Stroke', 'Diabetes', 'Dementia'))

# Now calculate prevalence by age group for each chronic disease
# prevalence = total / affected
# Diabetes
male_prev <- data.frame(colSums(mFEM_2014) / nrow(mFEM_2014))
female_prev <- data.frame(colSums(fFEM_2014) / nrow(fFEM_2014))
colnames(male_prev) <- 'FEM_male'
colnames(female_prev) <- 'FEM_female'
